The Astropy Project: \\ Sustaining and Growing a Community-oriented Open-source Project and the Latest Major Release (v5.0) of the Core Package

### 2022-01-25 src/ms.tex
Add initial JWST section

Software developers at the Space Telescope Science Institute (STScI),
the operations center of JWST, have been developing Python-based tools
for JWST since 2010 (starting with the JWST Calibration Reference Data
System) and have provided major contributions to \astropy from its
inception. The JWST instrument calibration pipelines, exposure-time
calculators, and data analysis tools are all written in Python and
depend on the \astropypkg core package and some coordinated and
affiliated packages. For the \astropypkg core package, the JWST mission
has provided extensive contributions to the \astropysubpkg{modeling},
\astropysubpkg{units}, \astropysubpkg{coordinates}, \astropysubpkg{wcs},
\astropysubpkg{io.fits}, \astropysubpkg{io.votable},
\astropysubpkg{stats}, \astropysubpkg{visualization}, and
\astropysubpkg{convolution} subpackages as well as to the general
package infrastructure and maintenance.

Likewise, JWST developers have provided significant contributions
to the \package{photutils} \citep{photutils}, \package{specutils}
\citep{specutils}, and \package{regions} \citep{regions} coordinated
packages and the \package{gwcs} \citep{gwcs} and \package{synphot}
\citep{synphot} affiliated packages. For example, development of the
\package{photutils} coordinated package for source detection and
photometry has largely been led by JWST contributions. JWST developers
have also made significant contributions to the \package{specutils}
coordinated package, which is used for analyzing spectroscopic data,
and the \package{regions} coordinated package, which is used to
handle geometric regions. The \package{gwcs} affiliated package for
generalized world coordinate systems was created specifically to handle
the complex world coordinate systems needed for JWST spectroscopic
data. The \package{synphot} affiliated package for synthetic photometry
was created at STScI and is a dependency of the JWST exposure-time
calculators. Further, the \package{ASDF} (Advanced Scientific Data
Format) package \citep{ASDF}, a next-generation interchange format for
scientific data, was initially developed at STScI to serialize JWST WCS
objects along with \astropypkg models, units, and coordinates. Over
its mission lifetime, JWST will continue its support in developing and
maintaining these critically dependent packages.

@@

\software{\package{astropy} \citep{astropy:2013, astropy:2018},
          \package{numpy} \citep{numpy:nature},
          \package{scipy} \citep{scipy},
          \package{matplotlib} \citep{matplotlib},
          \package{Cython} \citep{cython},
          \package{photutils} \citep{photutils},
          \package{specutils} \citep{specutils},
          \package{regions} \citep{regions},
          \package{gwcs} \citep{gwcs},
          \package{synphot} \citep{synphot},
          \package{ASDF} \citep{ASDF}.
        %   \package{SOFA} \citep{sofa},
        %   \package{ERFA} (\citealt{erfa})
          }

>>>>

Software developers at the Space Telescope Science Institute (STScI),
the operations center of JWST, have been developing Python-based tools
for JWST since 2010 (starting with the JWST Calibration Reference Data
System) and have provided major contributions to \astropy from its
inception. The JWST instrument calibration pipelines, exposure-time
calculators, and data analysis tools are all written in Python and
depend on the \astropypkg core package and some coordinated and
affiliated packages. For the \astropypkg core package, the JWST mission
has provided extensive contributions to the \astropysubpkg{modeling},
\astropysubpkg{units}, \astropysubpkg{coordinates}, \astropysubpkg{wcs},
\astropysubpkg{fits}, \astropysubpkg{votable}, \astropysubpkg{stats},
\astropysubpkg{visualization}, and \astropysubpkg{convolution}
subpackages as well as to the general package infrastructure and
maintenance.

Likewise, JWST developers have provided significant contributions to
the \package{photutils}, \package{specutils}, and \package{regions}
coordinated packages and the \package{gwcs} affiliated package. For
example, development of the \package{photutils} coordinated package
for source detection and photometry has largely been led by JWST
contributions. JWST developers have also made significant contributions
to the \package{specutils} coordinated package, which is used for
analyzing spectroscopic data, and the \package{regions} coordinated
package, which is used to handle geometric regions. The \package{gwcs}
affiliated package for generalized world coordinate systems was created
specifically to handle the complex world coordinate systems needed
for JWST spectroscopic data. Further, the \package{ASDF} (Advanced
Scientific Data Format) package, a next-generation interchange format
for scientific data, was initially developed at STScI to serialize JWST
WCS objects along with \astropypkg models, units, and coordinates. Over
its mission lifetime, JWST will continue its support in developing and
maintaining these critically dependent packages.

@@

\software{\package{astropy} \citep{astropy:2013, astropy:2018},
          \package{numpy} \citep{numpy:nature},
          \package{scipy} \citep{scipy},
          \package{matplotlib} \citep{matplotlib},
          \package{Cython} \citep{cython}.
        %   \package{SOFA} \citep{sofa},
        %   \package{ERFA} (\citealt{erfa})
          }
